Differentiable Neural Computers

### 2018-05-16 Presentation/Presentation.tex
?

\begin{frame}{Approach}
	Train a RNN to act as the \alert{controller} of a memory matrix M of N 
	addresses through R \alert{read heads} and one \alert{write head}.

	\pause
	\begin{enumerate}
	\item \alert{Content Lookup}\\
		\begin{itemize}
		\item \alert{Attention} over memory defined by weightings $w \in \mathcal{S}^N$
		\item Compare controller output with memory objects (\alert{auto-associative memory})
		\item Allow partial matches  (\alert{pattern completion})
		\end{itemize}
	\pause
	\item \alert{Sequential Retrieval}
		\begin{itemize} 
		\item Fill $L \in [0,1]^{N \times N}$ indexing \alert{temporal transitions}
		\item \alert{Shift} operations defined by $Lw,\ L^\top w$
		\end{itemize}
	\pause
	\item \alert{Dynamic Allocation}
		\begin{itemize}
		\item Mark memory locations with $\{0,1\}$ to \alert{signal usage}
		\item Manipulate signals during R/W operations to enable \alert{reallocation}
		\item Generalization to \alert{unbounded memory}
		\end{itemize}
	\end{enumerate}
\end{frame}

@@

	\alert{"Free list" scheme}
	\begin{align*}
	\pmb{\psi}_t &= \prod\limits_{i=1}^R (\pmb{1} - \pmb{\phi}_t^iw_{t-1}^{r,i}) \tag{\alert{memory retention}}\\
	u_t &= (\pmb{u}_{t-1} + \pmb{w}_{t-1}^w + \pmb{u}_{t-1} \circ \pmb{w}_{t-1}^w) \circ \pmb{\psi}_t \tag{\alert{usage tracking}}\\
	\end{align*}

@@

\begin{frame}{Memory Adressing: Temporal Linking}

\begin{frame}{Further Reading}
	\begin{itemize}
	\item \alert{Neural Turing Machines} (Graves, Wayne, Danihelka)
	\item \alert{Entity Networks} (Henaff, Weston, Szlam, Bordes, LeCun)
	\item \alert{End-to-End Memory Networks} (Sukhbaatar, Szlam, Weston, Fergus)	
	\item \alert{Jointly Learning to Align and Translate} (Bahdanau, Cho, Bengio)
	\item \alert{Principles of Probabilistic Programming Languages} (Goodman)
	\item \alert{Backprop as a Functor} (Fong, Spivak, Tuyéras)
	\item \alert{Formal Methods for Probabilistic Programming} (Selsam, Liang, Dill)
	\end{itemize}
\end{frame}

\begin{frame}{Conclusion}
	\alert{Takeaway}\\
	We can automatically infer simple functions over complex data structures in the form of \alert{probability distributions}, just by using examples!\\

	\pause
	\center	\alert{Thank you!}
\end{frame}

\begin{frame}{LSTM: State Equations}

	\begin{align}
	\ii_t^l &= \zeta_i(\mathcal{I}) \tag{\alert{input gate}}\\
	\ff_t^l &= \zeta_f(\mathcal{I})	\tag{\alert{forget gate}}\\
	\Cc_t^l &= \ff_t^l\Cc_{t-1}^l + \ii_t^l\zeta_c(\mathcal{I}) \tag{\alert{memory cell}}\\
	\oo_t^l &= \zeta_o(\mathcal{I})	\tag{\alert{output gate}}\\
	\hh_t^l &= \oo_t^l\zeta_h(\Cc_t^l)		\tag{\alert{hidden layer}}
	\end{align}
%	\nonumber \\ 
%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
%	\end{align}
%	\begin{align}
%	\ii_t^l &= \sigma(W_i^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_i^l)   \tag{\alert{input gate}}\\
%	\ff_t^l &= \sigma(W_f^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_f^l)	\tag{\alert{forget gate}}\\
%	\Ss_t^l &= \ff_t^l\Ss_{t-1}^l + \ii_t^ltanh(W_s^l[\xx_t;\hh_{t_1}^l;\hh_t^{l-1}] + \bb_s^l)		\tag{\alert{state}}\\
%	\oo_t^l &= \sigma(W_o^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_o^l)		\tag{\alert{output gate}}\\
%	\hh_t^l &= \oo_t^ltanh(\Ss_t^l)		\tag{\alert{hidden}}\\
%	\nonumber \\ 
%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
%	\end{align}
\end{frame}

>>>>

\begin{frame}{Approach}
	Train a RNN to act as the \alert{controller} of a memory matrix $M \in \mathbb{R}^{N\times W}$ through R \alert{read heads} and one \alert{write head}.

	\pause
	\begin{enumerate}
	\item \alert{Content Lookup}\\
		\begin{itemize}
		\item \alert{Attention} over memory defined by weightings $w \in \mathcal{S}^N$
		\item Compare controller output with memory objects (\alert{auto-associative memory})
		\item Allow partial matches  (\alert{pattern completion})
		\end{itemize}
	\pause
	\item \alert{Sequential Retrieval}
		\begin{itemize} 
		\item Fill $L \in [0,1]^{N \times N}$ indexing \alert{temporal transitions}
		\item \alert{Shift} operations defined by $Lw,\ L^\top w$
		\end{itemize}
	\pause
	\item \alert{Dynamic Allocation}
		\begin{itemize}
		\item Mark memory locations with $\pmb{u} \in [0,1]^N$ to \alert{signal usage}
		\item Manipulate signals during R/W operations to enable \alert{reallocation}
		\item Generalization to \alert{unbounded memory}
		\end{itemize}
	\end{enumerate}
\end{frame}

@@

	\alert{"Free list" scheme}
	\begin{align*}
	\pmb{\psi}_t &= \prod\limits_{i=1}^R (\pmb{1} - \pmb{\phi}_t^iw_{t-1}^{r,i}) \tag{\alert{memory retention}}\\
	u_t &= (\pmb{u}_{t-1} + \pmb{w}_{t-1}^w - \pmb{u}_{t-1} \circ \pmb{w}_{t-1}^w) \circ \pmb{\psi}_t \tag{\alert{usage tracking}}\\
	\end{align*}

@@

\begin{frame}{Memory Adressing: Temporal Linking}
	\alert{Read modes}: $\pmb{\pi}_t^i \in \mathcal{S}_3$\\

	\pause
	\alert{Temporal Transition} $\pmb{L}_t \in [0,1]^{N\times N}$
	\[
	\pmb{L}[i,j] = \underbrace{(1 - w_t^W[i] - w_t^W[j])\pmb{L}_{t-1}[i,j]}_{\text{\tiny{{Part of last transition}}}} + \underbrace{w_t^w[i]w_{t-1}^w[j]}_{\text{\tiny{Current transition}}}
%	\pmb{p}_t = (1 - \sum\limits_{i}\pmb{w}_t^W[i])\pmb{p}_{t-1} + \pmb{w}_t^W
	\]

	\pause
	\alert{Mode Interpolation}
	\[
	\pmb{w}_t^{r,i} = 
					\underbrace{\pmb{\pi}_t^i[1]L\pmb{w}_t^{r,i}}_{\text{\tiny{Forward shift}}} + 
					\underbrace{\pmb{\pi}_t^i[2]\pmb{w}_t^{r,i}}_{\text{\tiny{No shift}}} + 
					\underbrace{\pmb{\pi}_t^i[3]L^\top\pmb{w}_t^{r,i}}_{\text{\tiny{Backward shift}}} 
	\]
\end{frame}

\begin{frame}{Conclusion}
	\alert{Recap}\\
	We can simulate computation and expand upon it by using differentiable, continuous operations.

	\pause
	\alert{Takeaway}\\
	We can automatically infer simple functions over complex data structures in the form of \alert{probability distributions}, just by using examples!\\
\end{frame}

\begin{frame}{Appendix: LSTM Equations}

%	\begin{align}
%	\ii_t^l &= \zeta_i(\mathcal{I}) \tag{\alert{input gate}}\\
%	\ff_t^l &= \zeta_f(\mathcal{I})	\tag{\alert{forget gate}}\\
%	\Cc_t^l &= \ff_t^l\Cc_{t-1}^l + \ii_t^l\zeta_c(\mathcal{I}) \tag{\alert{memory cell}}\\
%	\oo_t^l &= \zeta_o(\mathcal{I})	\tag{\alert{output gate}}\\
%	\hh_t^l &= \oo_t^l\zeta_h(\Cc_t^l)		\tag{\alert{hidden layer}}
%	\end{align}
%	\nonumber \\ 
%	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
%	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
%	\end{align}
	\begin{align}
	\ii_t^l &= \sigma(W_i^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_i^l)   \tag{\alert{input gate}}\\
	\ff_t^l &= \sigma(W_f^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_f^l)	\tag{\alert{forget gate}}\\
	\Ss_t^l &= \ff_t^l\Ss_{t-1}^l + \ii_t^ltanh(W_s^l[\xx_t;\hh_{t_1}^l;\hh_t^{l-1}] + \bb_s^l)		\tag{\alert{state}}\\
	\oo_t^l &= \sigma(W_o^l[\xx_t;\hh_{t-1}^l;\hh_t^{l-1}]+\bb_o^l)		\tag{\alert{output gate}}\\
	\hh_t^l &= \oo_t^ltanh(\Ss_t^l)		\tag{\alert{hidden}}\\
	\nonumber \\ 
	\pmb{\upsilon}_t &= W_y[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{output vector}}\\
	\pmb{\xi}_t &= W_{\xi}[\hh_t^1;\dots;\hh_t^L]		\tag{\alert{interface vector}}
	\end{align}
\end{frame}

\begin{frame}{Appendix: Further Reading}
	\begin{minipage}{0.49\textwidth}
	\underline{\alert{Neural Architectures}}
	\begin{itemize}
	\item \alert{Learning to Forget}\\ (Gers, Schmidhuber, Cummins)
	\item \alert{Neural Turing Machines}\\ (Graves, Wayne, Danihelka)
	\item \alert{Entity Networks}\\ (Henaff, Weston, Szlam, Bordes, LeCun)
	\item \alert{End-to-End Memory Networks}\\ (Sukhbaatar, Szlam, Weston, Fergus)	
	%\item \alert{Jointly Learning to Align and Translate}\\ (Bahdanau, Cho, Bengio)
	%\item \alert{Principles of Probabilistic Programming Languages} (Goodman)
	%\item \alert{Backprop as a Functor} (Fong, Spivak, Tuyéras)
	%\item \alert{Formal Methods for Probabilistic Programming} (Selsam, Liang, Dill)
	\end{itemize}
	\end{minipage}
	\begin{minipage}{0.49\textwidth}
	\begin{itemize}	
	\item \alert{Jointly Learning to Align and Translate}\\ (Bahdanau, Cho, Bengio)
	\end{itemize}
	\underline{\alert{Probabilistic Programming}}
	\begin{itemize}
	\item \alert{Principles of Probabilistic Programming Languages} (Goodman)
	\item \alert{Backprop as a Functor} (Fong, Spivak, Tuyéras)
	\item \alert{Formal Methods for Probabilistic Programming} (Selsam, Liang, Dill)
	\end{itemize}
	\end{minipage}
\end{frame}
